# Aumann Econ Forecasting Homework 1

## 1) Source Description

-The data is on total job opening (non-farm) in the USA (in the thousands).

-The source of the data is from the [U.S. Bureau of Labor Statistics](https://fred.stlouisfed.org/series/JTSJOL), and is hosted on the FRED database maintained by the Federal Reserve Bank of St. Louis.

-This data is useful as an indicator for finding gaps in the demand for labor and could possible be quite useful as an indicator for labor shortages.

-A forecast could be used to find these future labor shortages and help create effective policy to avoid such shortcomings.

## 2) Job Openings Time Series Plot

```{r echo=FALSE}
dataset.csv = read.csv("https://raw.githubusercontent.com/LiamDavidAumann/Econ-Forecasting-ECON-686-/main/JobOpenings.csv", header = TRUE)
names(dataset.csv) = c("Date", "JobOpenings")

openings <- ts(dataset.csv[, "JobOpenings"], start = c(2000, 12), frequency = 12)

plot(openings, main="Job Openings: Non-Farm (in thousands)",
     ylab="Job Openings",
     lwd=1.4,
     cex=1.4)
```

## 3) Simple Forcasts

### Naive
This naive forecast was calculated by using the previous observation (in this case July 2022) to forecast for August and September 2022.        
  
**Step 1** (August 2022): 11,239

**Step 2** (September 2022): 11,239

### Seasonal Naive
This seasonal naive forecast was calculated by using the totals from Q4 2021 and Q1 2022 total to forecast for Q4 2022 and Q1 2023.       

-**Step 1** Q4 2022 (total): 33,464

-**Step 2** Q1 2023 (total): 34,482

### Averaging
This is the monthly average. In this case the average totals since 2001 for August and September respectively were calculated to create the forecast.    
-**Step 1** (August 2022):4855.7

-**Step 2** (September 2022):4887.3

## 4) Linear Time Trend
```{r, echo=FALSE}
library(tstools)

openings.trend <- make.trend(openings)
fitJob <- tsreg(openings, openings.trend)
fitJob
```

-**Step 1** (August 2022):

```{r echo=FALSE}
#Observation 261 would be August 2022
2364.88 + (20.25*261)
```

-**Step 2** (September 2022):
```{r echo=FALSE}
#Observation 262 would Septemeber 2022
2364.88 + (20.25*262)
```

The regression suggests an upward trend which is expected as job openings have been rising steadily since 2010.       
This expectation is only compounded by the characteristics of the post-COVID labor market.   


















