---
title: "Total Domestic Construction Spending "
output: html_document
---

This variable measures the total amount (in millions of dollars) spent on construction in the USA each month.  

```{r echo=FALSE}
library(tstools)
dataset.csv = read.csv("https://raw.githubusercontent.com/LiamDavidAumann/Econ-Forecasting-ECON-686-/main/constructionnotadjusted.csv", header = TRUE)
names(dataset.csv) = c("Date", "AmountSpent")

construct <- ts(dataset.csv[, "AmountSpent"], start = c(1993, 1), frequency = 12)

plot(construct, main="Total Domestic Construction Spending (unadjusted)",
     ylab="Total Construction Spending (in millions)",
     lwd=1.4,
     cex=1.4)
```

Although the plot clearly trends upward as time goes forward, each year in the data follows a similar "up/down" pattern.  

An annual seasonality is expected. Most construction happens in the summer and thus it is expected that construction spending will be high in the summer and low in the winter.      

```{r echo=FALSE}
dum_con <- month.dummy(construct, "Jan")
trend <- make.trend(construct)
rhs <- ts.combine(trend, dum_con)
fit_init <- tsreg(construct, rhs)

construct.dt <- fit_init$resids
plot(construct.dt, main="Total Domestic Construction Spending (adjusted)",
     ylab="Adjusted Construction Spending",
     lwd=1.4,
     cex=1.4)

```
  
## Forecast   

The time trend/seasonal component for September 2022 is: 

```{r echo=FALSE}
#Coefficients grabbed from fit_init
28085.8+222.8*(357)+21705.7
```

The time trend/seasonal component for Ocotber 2022 is: 

```{r echo=FALSE}
#Coefficients grabbed from fit_init
28085.8+222.8*(358)+20129.2
```
    
## Best Model   

Selected the best model by using the downward model selection method with the predictors: trend, March, April, May, June, July, August, September, October, November, and December.  

This model was selected with the AIC:
```{r echo=FALSE}
preds <- ts.combine(trend, dum_con)
#stepwise.selection(construct, preds, AIC)

#Fitb found using stepwise.selection() but most of the output makes the html garbled (this is why it is commented out)
fitb <- tsreg(construct, ts.combine(trend, dum_con[, c("Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")]))

AIC(fitb)
```

