---
title: "Lecture#5"
output: html_document
---

## R Markdown

FORMATS:

-Word
-HTML
-PDF
-Markdown

Used to export to other formats.
-use Knit

-orignal
-Github
-pandoc

R markdown calls Pandoc (check pandoc for documentation)

# Literate Programming 

- Write a document
- Have R code inside it
- Rus R code and inserts output for you
- Changes are ez pz
- Complete record of what you have done
- EZ verification
- EZ to collab
- Get distributable documents
-TLDR:
(code inside and the computer inserts it)

# Relationship between rainfall and harvest

`#` is a section heading

## Analysis 

### Description

Im working with harvest and rainfall data for the last few years.
This is a small dataset.

```{r}
#Three ticks indicate a code chunk {r} indicates it is r code and ``` stops the chunk

rain <- c(30,32,18,24,38,32)
harvest <- c(150,145,55,70,180,150)
plot(rain,harvest,ylim = c(0,200),xlim=c(0,50))
abline(a=-75,b=7)


mylm = lm(harvest ~ rain)
```

What about R code you don't wanna run?

```
lm(harvest ~ rain)
```
or:

The code was: `lm(harvest ~ rain)`


```{r, echo=FALSE}
#echo=FALSE disables the code from being shown and only shows the output
rain <- c(30,32,18,24,38,32)
harvest <- c(150,145,55,70,180,150)
plot(rain,harvest,ylim = c(0,200),xlim=c(0,50))
abline(a=-75,b=7)


mylm = lm(harvest ~ rain)
```

```{r, eval=FALSE}
#eval=FALSE only shows the code and not output
rain <- c(30,32,18,24,38,32)
harvest <- c(150,145,55,70,180,150)
plot(rain,harvest,ylim = c(0,200),xlim=c(0,50))
abline(a=-75,b=7)


mylm = lm(harvest ~ rain)
```

- *italics*
- **bold**
- Lists start with `- `
  - Sublist
  - Second sublist item
- Equations $y_{t}$
  - $\sum_{i=1}^{4}\xi_{i}$
- Line breaks

This is not
broken.

This is  
Broken.

#Estimating the Mean

```{r}
harvest <- c(150,145,55,70,180,150)
lm(harvest ~ 1)
#Give me an intercept and nothing else
#ctrl+shift+enter
#runs a chunk
```

# Steps Ahead
1) Forecast one step ahead: If data ends in Junly 2022, predict August 2022.
 
2) Forecast one step ahead: If data ends in Junly 2022, predict Septmber 2022.

```{r}
inflation <- read.csv("https://raw.githubusercontent.com/bachmeil/econ-686-fall-2022/main/inflation.csv", header=TRUE)
names(inflation) <- c("date","dcpi")
dcpi <- ts(inflation[, "dcpi"], start = c(1948, 1), frequency = 12)
library(tstools)
last(dcpi)
```

One step (August 2022): 8.5% (with naive approach)
Two step (Septmeber 2022): 8.5% (with naive still)


